Continuously Generalizing Buildings to Built-up Areas\\ by Aggregating and Growing

### 2017-10-16 ContinuousGeneralisation_Paper/ContinuousGeneralisation_Paper_Sigspatial/PaperBody.tex
improved some codes

\section{Case Study}
\label{sec:CaseStudy}
We have implemented our method based on
C\# (Microsoft Visual Studio 2015) and ArcObjects SDK 10.4.1. 
The code is available in open source on 
Github\footnote{\url{https://github.com/IGNF/Continuous-Generalisation}}.
The offsetting function and clipping function 
are available from library \textsc{Clipper} of \citet{Johnson2014}.
The offsetting function is used for the buffering, dilation, erodion, and merge operations.
An evaluation of \textsc{Clipper} can be found in \citet{Palfrader2015}.
We ran our case study under 64-bit 
Windows 7 on a 3.3 GHz dual core CPU with 8 GB RAM.
We measured processing time by the built-in C\# class 
\emph{Stopwatch}.
Our testing data is extracted from a dataset produced 
by the French Mapping Agency (IGN);
see \fig\ref{fig:Data}.
The data is at scale $1:15{,}000$, which means $M_\mathrm{s}=15{,}000$.
It represents the buildings of four towns, 
i.e., Aussevielle, Denguin,  Poey-de-Lescar, and Siros, 
in the Pyr\'en\'ees-Atlantiques county, south-western France.
IGN also stores a dataset at scale $1:50{,}000$.
This dataset was basically obtained from the data at scale $1:15{,}000$ 
by buffering with distance $25\,\mathrm{m}$,
where sometimes distance $50\,\mathrm{m}$ was also used
in order to identify towns.
A restriction for the town from \citet{Boffet2000} is that 
the longest edge in an MST of the buildings 
should be shorter than $100\,\mathrm{m}$.

@@

\begin{figure}[tb]
	\centering
	\begin{tikzpicture}[]
	\begin{axis}[
	height=5cm,
	width= \linewidth-0.1cm,
	axis lines = left,
	%	axis x line=center,
	%	axis y line=left,
	xtick={0.1,0.2,...,1},
	ytick={500,1000,...,3000},
	xlabel={$t$},
	ylabel={number of buildings},
	xlabel style={below right},
	%	ylabel style={at={(axis description cs:0,1.1)},rotate=270,anchor=north},
	xlabel style={at={(axis description cs:1,0)},anchor=north},
	%	ylabel style={above left},
	xmin=0,
	xmax=1.1,
	ymin=0,
	ymax=3200,
	cycle list name=black white,
	]
	\addplot+ [domain=0:1,samples=11] {2590*15/(15+35* x)};
%	\addplot+ [domain=0:1,samples=11] {2590* (15/(15+35* x))^1.5};
	\addplot+  coordinates {
		(0,2590)
		(0.1,1963)
		(0.2,758)
		(0.3,304)
		(0.4,177)
		(0.5,122)
		(0.6,92)
		(0.7,73)
		(0.8,66)
		(0.9,59)
		(1,56)		
	};
	\legend{\quad radical law, \quad our results}
	\end{axis}
	\end{tikzpicture}
	\caption{A comparison of the numbers of building between our results and 
		T\"opfer's radical law.}
	\label{fig:BuilidngNumber}
\end{figure}

>>>>

\section{Case Study}
\label{sec:CaseStudy}
We have implemented our method based on
C\# (Microsoft Visual Studio 2015) and ArcObjects SDK 10.4.1. 
The code is available in open source on 
Github\footnote{\url{https://github.com/IGNF/Continuous-Generalisation}}.
The offsetting function and clipping function 
are available from library \textsc{Clipper} of \citet{Johnson2014}.
The offsetting function is used for the buffering, dilation, 
erosion, and merge operations.
An evaluation of \textsc{Clipper} can be found in \citet{Palfrader2015}.
We ran our case study under 64-bit 
Windows 7 on a 3.3 GHz dual core CPU with 8 GB RAM.
We measured processing time by the built-in C\# class 
\emph{Stopwatch}.
Our testing data is extracted from a dataset produced 
by the French Mapping Agency (IGN);
see \fig\ref{fig:Data}.
The data is at scale $1:15{,}000$, which means $M_\mathrm{s}=15{,}000$.
It represents the buildings of four towns, 
i.e., Aussevielle, Denguin,  Poey-de-Lescar, and Siros, 
in the Pyr\'en\'ees-Atlantiques county, south-western France.
IGN also stores a dataset at scale $1:50{,}000$.
This dataset was basically obtained from the data at scale $1:15{,}000$ 
by buffering with distance $25\,\mathrm{m}$,
where sometimes distance $50\,\mathrm{m}$ was also used
in order to identify towns.
A restriction for the town from \citet{Boffet2000} is that 
the longest edge in an MST of the buildings 
should be shorter than $100\,\mathrm{m}$.

@@

%\begin{figure}[tb]
%	\centering
%	\begin{tikzpicture}[]
%	\begin{axis}[
%	height=5cm,
%	width= \linewidth-0.1cm,
%	axis lines = left,
%	%	axis x line=center,
%	%	axis y line=left,
%	xtick={0.1,0.2,...,1},
%	ytick={500,1000,...,3000},
%	xlabel={$t$},
%	ylabel={number of buildings},
%	xlabel style={below right},
%	%	ylabel style={at={(axis description 
%%cs:0,1.1)},rotate=270,anchor=north},
%	xlabel style={at={(axis description cs:1,0)},anchor=north},
%	%	ylabel style={above left},
%	xmin=0,
%	xmax=1.1,
%	ymin=0,
%	ymax=3200,
%	cycle list name=black white,
%	]
%	\addplot+ [domain=0:1,samples=11] {2590*15/(15+35* x)};
%%	\addplot+ [domain=0:1,samples=11] {2590* (15/(15+35* 
%%x))^1.5};
%	\addplot+  coordinates {
%		(0,2590)
%		(0.1,1963)
%		(0.2,758)
%		(0.3,304)
%		(0.4,177)
%		(0.5,122)
%		(0.6,92)
%		(0.7,73)
%		(0.8,66)
%		(0.9,59)
%		(1,56)		
%	};
%	\legend{\quad radical law, \quad our results}
%	\end{axis}
%	\end{tikzpicture}
%	\caption{A comparison of the numbers of building between our 
%results and 
%		T\"opfer's radical law.}
%	\label{fig:BuilidngNumber}
%\end{figure}
